%% The following is a directive for TeXShop to indicate the main file
%%!TEX root = diss.tex

\chapter{Acknowledgments}

First and most of all I'd like to thank my family. My parents, J.C. and Dorothea, your support has been completely indispensable. I am lucky to have such fantastic parents. My wife, Elizabeth, I started this PhD before I met you but I couldn't have finished it without you. 

I do believe I have had the best supervisory committee of anyone I know. Dr.\,Beatty, Dr.\,Murphy, and  Dr.\,Fernandez you have been the exactly perfect level of supportive, critical, and congratulatory. Thank you.

I have been incredibly fortunate to have been in the Smit lab. It has been said that choosing your supervisor is the most important choice you have to make in grad school---I chose well in John Smit. Dr.\,Smit, your patience with my crazy ideas let me grow as a scientist but your lack of patience with my crazy ideas kept me in line and prevented my PhD from lasting a decade. Dr.\,Nomellini, I have been fortunate to have you nearby to fix my mistakes, hear me complain about my mistakes, and showing me how to prevent future mistakes. The few other members of our lab that I have shared time with, Lyngrace, Jan, Christina, you have all been great allies in the lab.

Beyond the official credits that the are given, I want to acknowledge the incredible collaborators I have had since day one. 
Dr.\,Evgeny Vinogradov is the world's preeminent expert on bacterial polysaccharide analysis, there is quite literally no one that would have been a better collaborator for our lipopolysaccharide work. The Consortium for Functional Glycomics Core H at Emory Univeristy were incredibly easy to work with and even though our results with them were ultimately negative, the service they provide is an invaluable asset to the field. Dr.\,Martine Caroff has been a surprisingly helpful source of expertise and critique, especially critique.

The Murphy lab in our department of Microbiology and Immunology is the go to collaborators for protein X-ray crystallography, my experiences are evidence to why that is. All of them (Angele, Meghan, Slade, Jason, Catherine, Stephanie, Marek, Michael, Mariko) accepted me like a lab member from the start. Dr.\,Anson Chan was an exceptional partner for crystallography, his expertise kept us moving forward against a tough project. Especially I would like to thank Dr.\,Chan for staying up all night many times on our long data collection runs. Staying up late isn't so bad, but staying up late for poor results deserves commendation. 

Dr.\,Roland Benz was my only collaborator to initiate a collaboration with us. The porin project started as a side-project but it has become a nice little story that I am happy to have been apart of. Dr.\,Benz, I hope to actually meet you one day.

Lastly, I would like to acknowledge my department as a whole. This department has been incredibly supportive and warm. I feel with people like Darlene, Sue, and Dr.\,Gold guiding the ship, I never felt like we were going to crash. A special acknowledgment goes to Dr.\,Jan Burian, who was always around with encouragement and advice but especially for his organization of many departmental events and teams that brought together a cadre of scientists on the dodgeball court, on the softball diamond, and beyond the confines of campus.

