%% The following is a directive for TeXShop to indicate the main file
%%!TEX root = diss.tex

\chapter{Preface}
\begin{epigraph} 
\textit{``Plenum ingenni pudoris fateri per quos profeceris''}\\
(To own up to those who were the means of one's own achievements)\\
Pliny the Elder, Natural History
\end{epigraph} 

The contents contained herein are original work by or in collaboration with me,
the primary author, unless specified below.

\paragraph{Chapter 2} 
Portions of chapter 2 have been used for the preparation of a manuscript for
submission for publication. The work was done in collaboration with Dr.\,Anson
Chan. I preformed all the experiments and wrote the wrote the majority of the
manuscript. Dr.\,Chan assisted in the X-ray diffraction data collection, the
data evaluation and processing, and edited and provided feedback on the writing
of the manuscript. 

\paragraph{Chapter 3}
Portions of chapter 3 have been published; \fullcite{jones2015core}. The work was
done as a collaboration with Dr.\,Evgeny Vinogradov. Dr.\,Vinogradov was
responsible for the majority of the structural work: monosaccharide analysis,
methylation analysis, and \textsc{NMR} analysis, as well as the written
summaries of those methods. Dr.\,John Nomellini constructed the strain used,
JS1025. The cytokine and cell culture experiments were new additions not present
in any publication. The execution of the HEK-Blue assay was performed by Gyles Ifill. I was
responsible for the preparation of all the samples, experimental design, and
writing the manuscript. 

\paragraph{Chapter 4}
A version of chapter 4 has been submitted for publication. I was responsible for
the sample preparation, purification, and strain construction. The laboratory of
Dr.\,Roland Benz was responsible for synthetic membrane conductance experiments.
The writing was a split collaboration.